Multi-level modeling with Openflexo/\FML

### 2022-03-18 6-modelpresentation.tex
try to rephrase a paragraph

Our proposition relies on ontological instantiation as presented in
Fig.~\ref{fig:LinguisticAndOntologicInstantiation}, with a common root concept
\texttt{ModelingElement}. Two types of ontological instantiations are needed to
meet the requirements of the challenge. One provides that some instances
conform to only one type (\texttt{Process} and \texttt{Task} do respectively
conform to \texttt{ProcessType} and \texttt{TaskType}). While some entities
define their conformity to several types (\texttt{Actor} and \texttt{Artifact}
do respectively conform to several \texttt{ActorType} and
\texttt{ArtifactType}). These instantiations are respectively expressed using
the relations \texttt{type} and \texttt{types} between \texttt{Type},
\texttt{Instance} and \texttt{MultiInstance} concepts. In the diagram, the
realization of these relations are indicated by a derived relation,
\texttt{/type} or \texttt{/types}, as for example between \texttt{Process} and
\texttt{ProcessType} or between \texttt{Actor} and \texttt{ActorType}.

@@

The \texttt{Actor} concept defines a boolean attribute called
\texttt{isSenior}, while \texttt{TaskType} defines an additional
\texttt{isCritical} boolean attribute, indicating that some instances are
flagged as critical and must be performed by senior actors. To fulfill
\textbf{P9} requirement, a supplementary constraint is required for
\texttt{TaskType} and is captured through the following invariant expressed in
the \FML language:

\begin{lstlisting}
forEach (actor : allowedActors) {
    assert !isCritical | actor.isSenior
}
\end{lstlisting}

>>>>

Our proposition relies on ontological instantiation as presented in
Fig.~\ref{fig:LinguisticAndOntologicInstantiation}, with a common root concept
\texttt{ModelingElement}. Two types of ontological instantiations are needed to
meet the requirements of the challenge. 
The first one is characterized by the fact that instances conform to only one
type (\texttt{Process} and \texttt{Task} do respectively conform to
\texttt{ProcessType} and \texttt{TaskType}). While the second type of
ontological instantiations allows some entities to define their conformity to
several types (\texttt{Actor} and \texttt{Artifact} do respectively conform to
several \texttt{ActorType} and \texttt{ArtifactType}). 
%One provides that some instances
%conform to only one type (\texttt{Process} and \texttt{Task} do respectively
%conform to \texttt{ProcessType} and \texttt{TaskType}). While some entities
%define their conformity to several types (\texttt{Actor} and \texttt{Artifact}
%do respectively conform to several \texttt{ActorType} and
%\texttt{ArtifactType}). 
These instantiations are respectively expressed using
the relations \texttt{type} and \texttt{types} between \texttt{Type},
\texttt{Instance} and \texttt{MultiInstance} concepts. In the diagram, the
realization of these relations are indicated by a derived relation,
\texttt{/type} or \texttt{/types}, as for example between \texttt{Process} and
\texttt{ProcessType} or between \texttt{Actor} and \texttt{ActorType}.

@@

The \texttt{Actor} concept defines a boolean attribute called
\texttt{isSenior}, while \texttt{TaskType} defines an additional
\texttt{isCritical} boolean attribute, indicating that some instances are
flagged as critical and must be performed by senior actors. To fulfill
\textbf{P9} requirement, a supplementary constraint is required for
\texttt{TaskType} and is captured through the following invariant expressed in
the \FML language:
\begin{lstlisting}
forEach (actor : allowedActors) {
    assert !isCritical | actor.isSenior
}
\end{lstlisting}
